\begin{thebibliography}{99}
  \bibitem{kreith2000}
    F. Kreith,
    ``CRC Handbook of Thermal Engineering,''
    \emph{CRC Press},
    2000.

  \bibitem{huang2008}
    W. Huang, K. Sankaranarayanan, K. Skadron, R. J. Ribando, M. R. Stan,
    ``Accurate, Pre-RTL Temperature-Aware Design Using a Parameterized, Geometric Thermal Model,''
    \emph{IEEE Transactions on Computers},
    vol.~57, no.~9, pp.~1277--1288, September 2008.

  \bibitem{lu2004}
    Z. Lu, W. Huang, S. Ghosh, J. Lach, M. Stan, K. Skadron,
    ``Analysis of Temporal and Spatial Temperature Gradients for IC Reliability,''
    March 2004.

  \bibitem{srinivasan2004}
    J. Srinivasan , S. V. Adve , P. Bose , J. A. Rivers,
    ``The Impact of Technology Scaling on Lifetime Reliability,''
    \emph{International Conference on Dependable Systems and Networks},
    pp.~177--186, June 2004.

  \bibitem{liao2005}
    W. Liao, L. He, K. M. Lepak,
    ``Temperature and Supply Voltage Aware Performance and Power Modeling at Mictoarchitecture Level,''
    \emph{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems},
    vol.~24, no.~7, pp.~1042--1053, July 2005.

  \bibitem{coskun2006}
    A. K. Coskun, T. S. Rosing, K. Mihic, G. De Micheli, Y. Leblebici,
    ``Analysis and Optimization of MPSoC Reliability,''
    \emph{Journal of Low Power Electronics},
    vol.~, no.~1, pp.~56--69, 2006.

  \bibitem{liu2007}
    Y. Liu, R. P. Dick, L. Shang, H. Yang,
    ``Accurate Temperature-Dependent Integrated Circuit Leakage Power Estimation is Easy,''
    \emph{DATE'07},
    2007.

  \bibitem{huang2009}
    L. Huang, F. Yuan, Q. Xu,
    ``Lifetime Reliablity-Aware Task Allocation and Scheduling for MPSoC Platforms,''
    \emph{DATE'09},
    June 2009.

  \bibitem{xiang2010}
    Y. Xiang, T. Chantem, R. P. Dick, X. S. Hu, L. Shang,
    ``System-Level Reliability Modeling for MPSoCs,''
    \emph{CODES+ISSS'10},
    October 2010.

  \bibitem{thiele2011}
    L. Thiele, L. Schor, H. Yang, I. Bacivarov,
    ``Thermal-Aware System Analysis and Software Synthesis for Embedded Multi-Processors,''
    \emph{DAC'11},
    June 2011.

  \bibitem{rao2007}
    R. Rao, S. Vrudhula,
    ``Performance Optimal Processor Throttling Under Thermal Constraints,''
    \emph{CASES'07}
    Septermer--October, 2008.

  \bibitem{rao2009}
    R. Rao, S. Vrudhula,
    ``Fast and Accurate Prediction of the Steady-State Throughput of Multicore Processors Under Thermal Constraints,''
    \emph{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems},
    vol.~28, no.~10, pp. 1559--1572, October 2009.

  \bibitem{bao2010}
    M. Bao, A. Andrei, P. Eles, Z. Peng,
    ``Temperature-Aware Idle Time Distribution for Energy Optimization with Dynamic Voltage Scaling,''
    \emph{DATE'10},
    March 2010.

  \bibitem{jedec2010}
    JEDEC Solid State Technology Association,
    ``Failure Mechanisms and Models for Semiconductor Devices,''
    \emph{JEDEC Publication},
    November 2010.

  \bibitem{hieu2004}
    N. Van Hieu,
    ``Multilevel Interconnect Reliability on the Effects of Electro-Thermomechanical Stress,''
    2004.

  \bibitem{press2007}
    W. H. Press, S. A. Teukolsky, W. T. Vetterling, B. P. Flannery,
    ``Numerical Recipes: The Art of Scientific Computing,''
    \emph{Cambridge University Press},
    third edition, 2007.

  \bibitem{umfpack2004}
    T. A. Davis,
    ``Algorithm 832: UMFPACK, an unsymmetric-pattern multifrontal method,''
    \emph{ACM Transactions on Mathematical Software},
    vol.~30, no.~2, pp.~196--199, June 2004.

  \bibitem{mazancourt1983}
    T. De Mazancourt, D. Gerlic,
    ``The Inverse of a Block-Circulant Matrix,''
    \emph{IEEE Transactions on Antennas and Propagation},
    vol.~AP–31, no.~5, pp.~808–810, September 1983.

  \bibitem{vescovo1997}
    R. Vescovo,
    ``Inversion of Block-Circulant Matrices and Circular Array Approach,''
    \emph{IEEE Transactions on Antennas and Propagation},
    vol.~45, no.~10, pp.~1565-–1567, October 1997.

  \bibitem{stoer2002}
    J. Stoer, R. Bulirsch,
    ``Introduction to Numerical Analysis,''
    \emph{Springer-Verlag, New York},
    third edition, 2002.

  \bibitem{schmitz2004}
    M. T. Schmitz, B. M. Al-Hashimi, P. Eles,
    ``System-Level Design Techniques for Energy-Efficient Embedded Systems,''
    \emph{Kluwer Academic Publishers},
    2004.

  \bibitem{chang2006}
    S.-C. Chang, S.-Y. Deng, J. Y.-M. Lee,
    ``Electrical Characteristics and Reliability Properties of Metal-Oxide- Semiconductor Field-Effect Transistors with Dy2O3 Gate Dielectric,''
    \emph{Apply Physics Letters},
    no.~85, August 2006.

  \bibitem{ciappa2003}
    M. Ciappa, F. Carbognani, W. Fichtner,
    ``Lifetime Prediction and Design of Reliability Tests for High-Power Devices in Automotive Applications,''
    \emph{IEEE Transactions on Device and Materials Reliability},
    vol.~3, no.~4, pp.~191--196, December 2003.

  \bibitem{dick1998}
    R. P. Dick, D. L. Rhodes, W. Wolf,
    ``TGFF: Task Graphs for Free,''
    \emph{CODES/CASHE'98},
    March 1998.

  \bibitem{xie2006}
    Y. Xie, W.-L. Hung,
    ``Temperature-Aware Task Allocation and Scheduling for Embedded Multiprocessor Systems-on-Chip (MPSoC) Design,''
    \emph{Journal of VLSI Signal Processing},
    no.~45, pp.~177--189, 2006.

  \bibitem{ffmpeg2011}
    http://ffmpeg.mplayerhq.hu.

  \bibitem{benini2005}
    L. Benini, D. Bertozzi, A. Bogliolo, F. Menichelli,
    ``MPARM: Exploring the Multi-Processor SoC Design Space with SystemC,''
    \emph{Journal of VLSI Signal Processing Systems},
    vol.~41, no.~2, September 2005.

  \bibitem{deb2002}
    K. Deb, A. Pratap, S. Agarwal, T. Meyarivan,
    ``A Fast and Elitist Multiobjective Genetic Algorithm: NSGA-II,''
    \emph{IEEE Transactions on Evolutionary Computations},
    vol.~6, no.~2, April 2002.

\end{thebibliography}
